---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geojsonio

<!-- badges: start -->
[![R-CMD-check](https://github.com/ropensci/geojsonio/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/geojsonio/actions?query=workflow%3AR-CMD-check)
[![cran checks](https://cranchecks.info/badges/worst/geojsonio)](https://cranchecks.info/pkgs/geojsonio)
[![R-CMD-check-docker](https://github.com/ropensci/geojsonio/workflows/R-CMD-check-docker/badge.svg)](https://github.com/ropensci/geojsonio/actions?query=workflow%3AR-CMD-check-docker)
[![codecov.io](https://codecov.io/github/ropensci/geojsonio/coverage.svg?branch=main)](https://codecov.io/github/ropensci/geojsonio?branch=main)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/geojsonio)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/geojsonio)](https://cran.r-project.org/package=geojsonio)
[![Codecov test coverage](https://codecov.io/gh/ropensci/geojsonio/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ropensci/geojsonio?branch=main)
[![R-CMD-check](https://github.com/ropensci/geojsonio/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/geojsonio/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE
)
```


__Convert various data formats to GeoJSON or TopoJSON__

This package is a utility to convert geographic data to GeoJSON and TopoJSON formats. Nothing else. We hope to do this one job very well, and handle all reasonable use cases.

Functions in this package are organized first around what you're working with or want to get, GeoJSON or TopoJSON, then convert to or read from various formats:

* `geojson_list()`/`topojson_list()` - convert to GeoJSON/TopoJSON as R list format
* `geojson_json()`/`topojson_json()` - convert to GeoJSON/TopoJSON as JSON
* `geojson_sp()` - convert output of `geojson_list()` or `geojson_json()` to `sp` spatial objects
* `geojson_sf()` - convert output of `geojson_list()` or `geojson_json()` to `sf` objects
* `geojson_read()`/`topojson_read()` - read a GeoJSON/TopoJSON file from file path or URL
* `geojson_write()`/`topojson_write()` - write a GeoJSON/TopoJSON file locally

Each of the above functions have methods for various objects/classes, including `numeric`, `data.frame`, `list`, `SpatialPolygons`, `SpatialLines`, `SpatialPoints`, etc.

Additional functions:

* `map_gist()` - push up a GeoJSON or topojson file as a GitHub gist (renders as an interactive map)
* `map_leaf()` - create a local interactive map using the `leaflet` package

## \*json Info

* GeoJSON - [spec](https://tools.ietf.org/html/rfc7946)
* [GeoJSON lint](https://geojsonlint.com/)
* TopoJSON - [spec](https://github.com/topojson/topojson-specification/blob/master/README.md)


## Install

A note about installing `rgeos` - built on top of C libraries, and installation often causes trouble for Linux users because no binaries are provided on CRAN for those platforms. Other dependencies in `geojsonio` should install easily automatically when you install `geojsonio`.

_Mac_

Install `GDAL` on the command line first, e.g., using `homebrew`

```
brew install gdal
```

Then install `rgeos`

```{r}
install.packages("rgeos", type = "source")
```

_Linux_

Get deps first

```
sudo apt-get install libgdal1-dev libgdal-dev libgeos-c1 libproj-dev
```

> Note: if you have trouble installing rgeos, try installing `libgeos++-dev`

Then install `rgeos`

```{r}
install.packages("rgeos", type = "source")
```

__Install geojsonio__

Stable version from CRAN

```{r}
install.packages("geojsonio")
```

Or development version from GitHub

```{r}
install.packages("remotes")
remotes::install_github("ropensci/geojsonio")
```

```{r}
library("geojsonio")
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/geojsonio/issues).
* License: MIT
* Get citation information for `geojsonio` in R doing `citation(package = 'geojsonio')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
