<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{geojsonio vignette}
-->

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

gistr vignette
==============

`geojsonio` converts geographic data to geojson and topojson formats. Nothing else. We hope to do this one job very well, and handle all reasonable use cases.

Functions in this package are organized first around what you're working with or want to get, geojson or topojson, then convert to or read from various formats:

* `geojson_list()`/`topojson_list()` - convert to geojson/topojson as R list format
* `geojson_json()`/`topojson_json()` - convert to geojson/topojson as json
* `geojson_read()``topojson_read()` - read a geojson/topojson file from file path or URL
* `geojson_write()` - write a geojson file locally (no write topojson yet)

Each of the above functions have methods for various objects/classes, including `numeric`, `data.frame`, `list`, `SpatialPolygons`, `SpatialLines`, `SpatialPoints`, etc.

Additional functions:

* `map_gist()` - push up a geojson or topojson file as a GitHub gist (renders as an interactive map)

## Install

A note about installing `rgdal` and `rgeos` - these two packages are built on top of C libraries, and their installation often causes trouble for Mac and Linux users because no binaries are provided on CRAN for those platforms. Other dependencies in `geojsonio` should install easily automatically when you install `geojsonio`. Change to the version of `rgdal` and `GDAL` you have):

_Mac_

Install `GDAL` on the command line first, e.g., usingn `homebrew`

```
brew install gdal
```

Then install `rgdal` and `rgeos`

```{r eval=FALSE}
install.packages("rgdal", type = "source", configure.args = "--with-gdal-config=/Library/Frameworks/GDAL.framework/Versions/1.11/unix/bin/gdal-config --with-proj-include=/Library/Frameworks/PROJ.framework/unix/include --with-proj-lib=/Library/Frameworks/PROJ.framework/unix/lib")
install.packages("rgeos", type = "source")
```

_Linux_

Get deps first

```
sudo apt-get install libgdal1-dev libgdal-dev libgeos-c1 libproj-dev
```

Then install `rgdal` and `rgeos`

```{r eval=FALSE}
install.packages("rgdal", type = "source")
install.packages("rgeos", type = "source")
```

__Install geojsonio__

Stable version from CRAN

```{r eval=FALSE}
install.packages("geojsonio")
```

Development version from GitHub

```{r eval=FALSE}
devtools::install_github("ropensci/geojsonio")
```

```{r}
library("geojsonio")
```

## GeoJSON

### Convert various formats to geojson

From a `numeric` vector of length 2

as _json_

```{r}
geojson_json(c(32.45, -99.74))
```

as a __list__

```{r output.lines=1:10}
geojson_list(c(32.45, -99.74))
```

From a `data.frame`

as __json__

```{r}
geojson_json(us_cities[1:2, ], lat = 'lat', lon = 'long')
```

as a __list__

```{r output.lines=1:10}
geojson_list(us_cities[1:2, ], lat = 'lat', lon = 'long')
```

From `SpatialPolygons` class

```{r}
library('sp')
poly1 <- Polygons(list(Polygon(cbind(c(-100, -90, -85, -100),
  c(40, 50, 45, 40)))), "1")
poly2 <- Polygons(list(Polygon(cbind(c(-90, -80, -75, -90),
  c(30, 40, 35, 30)))), "2")
sp_poly <- SpatialPolygons(list(poly1, poly2), 1:2)
```

to __json__

```{r}
geojson_json(sp_poly)
```

to a __list__

```{r output.lines=1:10}
geojson_list(sp_poly)
```

From `SpatialPoints` class

```{r}
x <- c(1, 2, 3, 4, 5)
y <- c(3, 2, 5, 1, 4)
s <- SpatialPoints(cbind(x, y))
```

to __json__

```{r}
geojson_json(s)
```

to a __list__

```{r output.lines=1:10}
geojson_list(s)
```

### Combine objects

`geo_list` + `geo_list`

> Note: `geo_list` is the output type from `geojson_list()`, it's just a list with a class attached so we know it's geojson :)

```{r output.lines=1:10}
vec <- c(-99.74, 32.45)
a <- geojson_list(vec)
vecs <- list(c(100.0, 0.0), c(101.0, 0.0), c(100.0, 0.0))
b <- geojson_list(vecs, geometry = "polygon")
a + b
```

`json` + `json`

```{r}
c <- geojson_json(c(-99.74, 32.45))23
vecs <- list(c(100.0, 0.0), c(101.0, 0.0), c(101.0, 1.0), c(100.0, 1.0), c(100.0, 0.0))
d <- geojson_json(vecs, geometry = "polygon")
c + d
```

### Write geojson

```{r}
geojson_write(us_cities[1:2, ], lat = 'lat', lon = 'long')
```

## Topojson

In the current version of this package you can read topojson. Writing topojson was in this package, but is gone for now - will come back later as in interface to [topojson](https://github.com/mbostock/topojson) via [V8](https://github.com/jeroenooms/V8).

Read from a file

```{r eval=FALSE}
file <- system.file("examples", "us_states.topojson", package = "geojsonio")
out <- geojson_read(file)
```

Read from a URL

```{r eval=FALSE}
url <- "https://raw.githubusercontent.com/shawnbot/d3-cartogram/master/data/us-states.topojson"
out <- topojson_read(url)
```

Or use `as.location()` first

```{r eval=FALSE}
(loc <- as.location(file))
out <- topojson_read(loc)
```

## To do

* Replace `rgdal` with javascript libraries to read from various file types (kml, shp, etc.) and convert to geojson. This is in development, and will come in the next version of this package most likely. 
* Performance improvements. Some operations already use the gdal or geos C libraries, so are quite fast, though the round trip to disk and back does take significant time. 
* More input types. We already have operations (json, list, etc.) for lots of input types (data.frame, list, sp classes). but likely there will be more added. 
